---
title: "Q2 Answer"
author: "Boray Yurdakul - ETM58d - Spring 2020"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Codes for answer of Question 2](https://github.com/ETM-58D/spring20-borayyurdakul/blob/master/files/q2.rtf)

    Question 2: Please use Boston house price dataset on https://www.cs.toronto.edu/~delve/data/boston/desc.html. “This dataset contains information collected by the U.S Census Service concerning housing in the area of Boston Mass.” and the details are provided on https://www.cs.toronto.edu/~delve/data/boston/bostonDetail.html. Suppose our aim is to understand if certain variables explains the variability better than the other. We would like to generate an index that can summarize the houses using few variables combined as an index. Perform PCA on the provided data and comment on your results.