---
title: "Q1 Answers"
author: "Boray Yurdakul - ETM58d - Spring 2020 - Corona Term lol"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Codes for answer of Question 1.a](files/q1a.html)

    This example is important because it is an R Notebook on Titanic data set. Titanic is considered as one of the Data Science 101 data set and this notebook provides a good exploratory data analysis. It is also a Kaggle Kernel, which is a very good source for this kind of example R codes. The notebook also covers feature engineering, missing data imputation and modeling.
    
2. [Codes for answer of Question 1.b](files/q1b.html)

    This example is important because it is an R Notebook on Titanic data set. Titanic is considered as one of the Data Science 101 data set and this notebook provides a good exploratory data analysis. It is also a Kaggle Kernel, which is a very good source for this kind of example R codes. The notebook also covers feature engineering, missing data imputation and modeling.
    
3. [Codes for answer of Question 1.c](files/q1c.html)

    This example is important because it is an R Notebook on Titanic data set. Titanic is considered as one of the Data Science 101 data set and this notebook provides a good exploratory data analysis. It is also a Kaggle Kernel, which is a very good source for this kind of example R codes. The notebook also covers feature engineering, missing data imputation and modeling.