---
title: "Q2 Answer"
author: "Boray Yurdakul - ETM58d - Spring 2020"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Codes for answer of Question 2](https://github.com/ETM-58D/spring20-borayyurdakul/blob/master/files/q2.rtf)

    After, we upload the data and giving the column names, we analyzed the scatterplot for all futures. We see that according to plots, there are correlation between NOX and DIS, MEDV and RM, LSTAT and MEDV.
    
    Later, we applied pca to our data and had an outcome. As we see in the class, we can determine a threshold value for variance. If we determine a threshold value of 0.85, we can take comp6. Outcome showed us that cumulative proportion of variance.
    
    Later, we analyzed the barplot of comp6 and coefficients. Comp6 used crim, zn, cas, nox, rm, rad, tax, ptratip, b for the equation and some of them have negative effect. For example, for the 1st observation, positive effect is bigger than the negative effect which means that with correlations crim+zn+nox+rad+tax+b is bigger than others.
    
    Please click [here](https://github.com/ETM-58D/spring20-borayyurdakul/blob/master/files/q2-q3.docx) for plots and more details.