---
title: "Q3 Answer"
author: "Boray Yurdakul - ETM58d - Spring 2020"
---
```{r,echo=FALSE,results="hide"}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```

```{r,echo=FALSE,eval=FALSE}
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="pdf_document")
rmarkdown::render("/home/baydogan/Courses/IE582/Fall18/Guidelines/example_homework_0.Rmd",output_format="html_document")
```

1. [Codes for answer of Question 3](https://github.com/ETM-58D/spring20-borayyurdakul/blob/master/files/q3.rtf)

    library(dplyr)
    library(data.table)

    After we upload the data, we identified the column names as movie names. We changed 0 values to NA values to fill the data with mean value for each column. We used dplyr package to fill the NA values and as we mentioned before we fill each column with its mean values. We took the transpose of the data to create a square matrix. Then, we applied distance function to data and created a matrix. We applied cmd to the matrix and drew the plot. It is very hard to make comments on plot.
    
    Please click [here](https://github.com/ETM-58D/spring20-borayyurdakul/blob/master/files/q2-q3.docx) for plots and more details.